About {\bf llvm2aa}

### 2011-08-29 v2/llvmbc2Aa/docs/llvm2aa.tex
added --pipedepths option to llvm2aa

The options:
\begin{itemize}
\item {\bf -modules=listfile} : Specify the list of functions in the bytecode
which should be converted to \Aa.   The names of these functions should be
listed in the text-file listfile. If this option is not specified, all functions
are converted.
\item {\bf -storageinit} :  Storage objects in the llvm bytecode
are explicitly initialized in the generated \Aa code.   An initializer
routine {\bf global\_storage\_initializer\_} is instantiated in
the \Aa code for this purpose.
\item {\bf llvm2aa} uses the LLVM compiler
infrastructure to perform LLVM byte-code optimizations.  A large list
of these optimizations is available through the llvm2aa command-line.
For more details, see LLVM documentation at http://www.llvm.org.
\end{itemize}

>>>>

The options:
\begin{itemize}
\item {\bf --modules=listfile} : Specify the list of functions in the bytecode
which should be converted to \Aa.   The names of these functions should be
listed in the text-file listfile. If this option is not specified, all functions
are converted.
\item {\bf --storageinit} :  Storage objects in the llvm bytecode
are explicitly initialized in the generated \Aa code.   An initializer
routine {\bf global\_storage\_initializer\_} is instantiated in
the \Aa code for this purpose.
\item {\bf -pipedepths=depthfile} : Specify the maximum depths of
pipes in the generated Aa program. The file ``depthfile'' is a list
of pairs (one pair per line).  The first element of the pair specifies
a pipe name, and the second, its maximum depth.   The default depth
of any pipe is $1$.
\item {\bf llvm2aa} uses the LLVM compiler
infrastructure to perform LLVM byte-code optimizations.  A large list
of these optimizations is available through the llvm2aa command-line.
For more details, see LLVM documentation at http://www.llvm.org.
\end{itemize}
